Something about Continuous Deductive Reasoning over Streamed RDF Data, maybe claim Soundness or some other Theoretical Quality

### 2015-06-18 content/contribution/CoDeR.tex
started fleshing out the data model: starting from the form of the model and working back to the semantics expressed, rather than starting with the semantics and working forward to the form of the model (see firstDraft copy)

	% Stream-based Data Model

>>>>

	% Stream-based Data Model
	The data model of CoDeR is composed of two classes of streams.
	The first are \emph{input}/\emph{output} streams, and provide the semantics of streams $S$, $P$ and $N$ for any ${CDP}$ expressed by a CoDeR-based system;
	they are sequences of instances of RDF triples, where an instance of an RDF triple is an RDF triple annotated with the time interval for which it is valid \citep{SemanticStreamingManagement,sparkwave} according to the ${CDP}$ expressed: ${\langle (s,p,o),i_{e},i_{n} \rangle}$.
	This interval for any entailed fact instance is derived from the valid time intervals of the fact instances that justify it, as shown in \reffig{intersected-intervals}:
	\begin{figure}[t]
		\centering
		\includegraphics[width=0.45\textwidth]{intersected-intervals}
		\caption{Derivation of valid-time for entailed fact instance from those of its justifying fact instances.}
		\labelfig{intersected-intervals}
	\end{figure}
	if ${A = \{c\,\text{:-}\,a\,,\,b\,.\}}$ and ${W^{S,3}_{2} = \{ \langle a,1,3 \rangle , \langle b,2,4 \rangle \}}$, then ${CDP_{2} = A \cup W^{S,3}_{2} \vDash \{ \langle a,1,3 \rangle , \langle b,2,4 \rangle , \langle c,2,3 \rangle \}}$, where $a$, $b$ and $c$ are RDF triples.
	It is in the base case of this derivation that the semantic window range $R$ of a ${CDP}$ is expressed:
	each fact instance arriving on an \emph{input} stream has a valid interval from the time of its arrival at the system for the duration of the semantic window expressed by that range $R$.

	Given that the ordering of instances in the \emph{output} stream by the value of $i_{e}$ yields the sequence of instances in the semantic stream $P$ entailed by a ${CDP}$, and that their ordering by the value of $i_{n}$ yields the sequence of instances in the semantic stream $N$, this gives all streams of CoDeR a dual semantics with respect to Continuous Datalog.
